\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-10 poster/main.tex
update poster

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} gives us the concrete probabilities of outputting candidates with certain Hellinegr distance from the correct posterior in 2 and 3 respectively.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.317\textwidth]{poster_6.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{The concrete outputting probabilities under different dimensions with data set of size $600$}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

@@

\begin{itemize}
  \item The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
  approach  when the latter uses a sensitivity proportional to dimensionality.
  \item From experimental results, the outperformance happens when the data size is greater than $400$ .
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

>>>>

Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} give us the discrete probabilities. On the x-axis: the distance of a potential output r from the true answer and on y-axis the probability of r being output by the mechanisms.
\begin{figure}[H]
\begin{center}
\centering
   \subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.317\textwidth]{poster_6.eps}
  \label{subfig_prior}
  }
  \subfigure[2 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_4.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_3d}
  } 
\caption{4-quantile and discrete probability plots}
\label{fig_concrete_prob}
\end{center}
\end{figure}
\scriptsize{Experiments above are with unit prior $\betad(1,1), \betad(1,1,1)$ and $\betad(1,1,1,1)$ (except Fig. \ref{subfig_prior}) , balanced datasets, $\epsilon = 1.0$ and $\delta = 10^{-8}$.}
\end{block}

@@

\begin{itemize}
  \item[-] The smoothed Hellinger distance based exponential mechanism outperforms asymptotically the baseline 
  approach  when the latter uses a sensitivity proportional to dimensionality.
  \item[-] From experimental results, the outperformance happens when the data size is greater than $400$ .
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.
